Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-01 paper/abstract.tex
First draft

\begin{abstract} 
    The Bayesian optimization has recently shown promising performance for
    automated analog circuit design. However, the sequential property of
    Bayesian optimization limits its further application. In this paper, a
    batched bayesian optimization method is proposed, the parallelization is
    realized via a multi-objective ensemble of acquisition functions. In each
    iteration, multiple acquisition functions are selected, the multi-objective
    optimization is then performed to search for the Pareto front of the
    acquisition functions, candidate points are then sampled from the Pareto
    fronts. The proposed method is compared with several state-of-the-art
    batched Bayesian optimization algorithms using analytical benchmark
    functions and real-world analog circuits; the experimental results show
    that the proposed method is competitive compared to the state-of-the-art
    methods.
\end{abstract}

>>>>

\begin{abstract} 
    The Bayesian optimization has recently shown promising performance for
    automated analog circuit design. However, the sequential property of
    Bayesian optimization limits its further application. In this paper, a
    batched bayesian optimization method is proposed, the parallelization is
    realized via a multi-objective ensemble of acquisition functions. In each
    iteration, multiple acquisition functions are selected, the multi-objective
    optimization is then performed to search for the Pareto front of the
    acquisition functions, candidate points are then sampled from the Pareto
    front. The proposed method is compared with several state-of-the-art
    batched Bayesian optimization algorithms using analytical benchmark
    functions and real-world analog circuits; the experimental results show
    that the proposed method is competitive compared to the state-of-the-art
    methods.
\end{abstract}

### 2018-02-01 paper/background.tex
Paper update
First draft

\subsection{Formulation}

@@

where $\bm{x} \in \textrm{D} \subset \textrm{R}^d$ is the design variables
and $f_i(\bm{x})$ represents the $i$-th cared circuit performance like gain
or phase margin of an amplifier. and the $\mathrm{FOM}(\bm{x})$ is the
design objective. Given the design parameters $\bf{x}$, the FOM value can be
obtained via circuit simulation using softwares like HSPICE or spectre.

@@

\textcolor{red}{ALERT: COPIED FROM MY PAPER SUMBITTED TO DAC}

>>>>

\subsection{Problem Formulation}

@@

where $\bm{x} \in \textrm{D} \subset \textrm{R}^d$ is the design variables
and $f_i(\bm{x})$ represents the $i$-th cared circuit performance like gain
or phase margin of an amplifier. and the $\mathrm{FOM}(\bm{x})$ is the
design objective. Given the design parameters $\bm{x}$, the FOM value can be
obtained via circuit simulation using softwares like HSPICE or spectre.

@@

### 2018-02-01 paper/mace.tex
Paper update
First draft

\textcolor{red}{ALERT: COPIED FROM MY TCAS-I paper}

@@

\subsection{MACE}

@@

With multi-objective optimization, the disagreement between different
acquisition function can be used for the parallelization of Bayesian
optimization, as best trade-off between these acquisition functions can be
captured by the Pareto front.

>>>>

@@

\subsection{Batched Bayesian Optimization via Multi-objective Acquisition Ensemble}

@@

With multi-objective optimization, the disagreement between different
acquisition functions can be used for the parallelization of Bayesian
optimization, as best trade-off between these acquisition functions can be
captured by the Pareto front.
